The pollination trade-off

### 2019-02-27 paper/manuscript.Rmd
Changes to first three paragraphs of intro

Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
<!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
Alongside the direct mutualisms between plants and their pollinators, the support to biodiversity can be achieved as a result of inter-species facilitation—the positive feedback loops that exist between plants that share pollinators or pollinators that share plant [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008]. 
In sum, inter-species facilitation is able to promote species coexistence because it is able to offset the effects of direct competition for resources [@stachowicz_mutualism_2001]. 
What is more, studies that are fundamental to our current knowledge of mutualism predict that the maximum number of coexisting species---effectively an upper limit to biodiversity---is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009]. 
And yet, not every pollinator species in natural communities interacts with every species of plant.

One explanation is that sharing a mutualistic partner also has costs [@waser_interspecific_1978]. 
As soon as there are costs, plants start competing for mutualistic partners, even if this competition is not strong enough to produce a net negative effect in fitness. 
It has been clear for a long time [@robertson_philosophy_1895; both experimentally @lewis_experimental_1961 and theoretically @levin_competition_1970] that when competition is strong enough, it can be detrimental to plants' fitness. 
So much so that competition for pollination has been shown to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
It is less clear, however, how exactly these strategies of differentiation, in turn, modulate the strength of competition for pollinators. 
<!-- The ecological factors that modulate the strength of competition, andfactors  -->
<!-- In addition, it has been shown that the strength of competition for pollinator can be modulated by multiple ecological factors factors (like the number of shared pollinators, the plants' relative abundance, visitor fidelity, and traits) [@bobisud_pollinator_1975; @mitchell_new_2009; @morales_interspecific_2008; @feinsinger_effects_1987; @campbell_pollinator_1985].  -->

There are two main mechanisms through which factors of ecological differentiation can affect plant fertilization [@morales_interspecific_2008]. 
The first mechanism, is by reducing the number of conspecific pollen grains on stigmas. 
For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of conspecific pollen deposited by animals---for those less attractive [@yang_pollinator_2011]. 
This can be seen as the *quantity* of the pollination service.
More subtly, when plants employ reproductive strategies that imply sharing pollination partners, even receiving a visit might not translate into fertilization.
This so because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species. 
This second mechanism, is called interspecific pollen transfer [@campbell_mechanism_1985]. 
Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the quantity and quality of pollination---and its relationship to competition vs. facilitation in pollination systems---is based mostly on studies of two plant species. 
However, competitive interactions between species pairs do not occur in isolation.

>>>>

Animal pollination systems play a disproportionally important role in food production and maintenance of global biodiversity [@bascompte_plant-animal_2007; @klein_importance_2007; @ollerton_how_2011]. 
<!-- FDO: Asked coauthors for a reference for the following statement but no-one provided. Therefore removing -->
Alongside the direct mutualisms between plants and their pollinators, biodiversity can be supported as a result of inter-species "facilitation"—the positive feedback loops that exist between plant species that share pollinators or pollinators that share plants [@moeller_facilitative_2004; @ghazoul_floral_2006; @molina-montenegro_positive_2008]. 
This inter-species facilitation is able to promote species coexistence by offsetting the effects of direct resource competition [@stachowicz_mutualism_2001]. 
Indeed, studies at the core of our current theoretical knowledge of mutualisms predict that the maximum number of coexisting species is achieved when the number of shared mutualistic partners is maximised in a community [@bastolla_architecture_2009].

However, in natural communities, plants rarely share all available pollinators.
One explanation is that plants are effectively competing for mutualistic partners because there is a *trade-off* between the benefits gained from maximising the number of mutualistic partners and the costs of sharing them with other plant species [@waser_interspecific_1978]. 
It has been clear for a long time [both experimentally and theoretically; @robertson_philosophy_1895; @lewis_experimental_1961; @levin_competition_1970] that when competition for pollination is strong enough, it can be detrimental to plants' fitness. 
In fact, it can be sufficient to drive ecological differentiation [for example by driving the evolution of of both traits and reproductive strategies; @mitchell_new_2009; @caruso_competition_2000]. 
It is less clear, however, how exactly ecological differentiation, in turn, affect the trade-off between facilitation and competition that is involved in the pollination service.

There are two main mechanisms through which competition for pollinators can affect plant fertilization [@morales_interspecific_2008]. 
The first, is by reducing the number of conspecific pollen grains on stigmas. 
For example, plants with distinctively attractive flowers might reduce the number of visits---and hence the amount of *conspecific* pollen deposited by animals---to those less attractive neighbouring plants [@yang_pollinator_2011]. 
This can be seen as the *quantity* of the pollination service.
More subtly, when plants employ reproductive strategies that imply sharing pollination partners, even receiving a visit might not translate into fertilization.
This so because a focal plant might receive pollen from a different species, or conversely, pollen from the focal plant might be lost to different species. 
This second mechanism, is called interspecific pollen transfer [@campbell_mechanism_1985]. 
Generally speaking, the higher the proportion of conspecific relative to heterospecific pollen the higher the *quality* of the pollination service. 
With few exceptions [@rathcke_interactions_1988; @lopezaraizamikel_impact_2007; @tur_evaluating_2016; @hegland_relative_2009; @aizen_reproductive_2010], most of what we know about the quantity and quality of pollination---and its relationship to competition vs. facilitation in pollination systems---is based mostly on studies of two plant species. 
However, competitive interactions between species pairs do not occur in isolation.
